---
title       : Diamonds Explorer 
subtitle    : Course Project for Developing Data Products
author      : Neelajit Chandra
framework   : io2012        
highlighter : highlight.js  
hitheme     : tomorrow       
widgets     : []            
mode        : selfcontained 
knit        : slidify::knit2slides
---

## Slide 1


> This slidify presentation serves as a reproducible pitch for the Course Project of Developing Data Products course offered by Johns Hopkins University on Coursera.  


> The objective of the project is to build a Shiny app and deploy it online.

---

## Slide 2

> The app that has been developed is a visualization tool which generates dot-plots between various variables of the `Diamonds` dataset, part of the `ggplot2` package.  

> The dot-plots are also generated using the `ggplot2` package. 

> The Shiny app has a slider input feature to select the number of observations ranging from 1000 to 53940.  

> Features like color and facets can also be used to segregate the resulting plots on the basis of the various aspects of the diamonds dataset.

---

## Slide 3

Summary of the `Diamonds` dataset.

```{r set-options, echo=FALSE}
options(width = 100)

library(ggplot2)

summary(diamonds)

```


---

## Slide 4

An example of the plot generated by the app.

```{r, echo=FALSE}
library(ggplot2)

p <- ggplot(data = diamonds, aes(x = carat, y = cut)) +
  geom_point() + aes_string(color = diamonds$clarity) +
  facet_grid(.~ color) + scale_size(c(2,4,6))

print(p)
```

